Supplementary material S3: ?

### 2019-01-11 Cover letter.Rmd
# Draft 0.1.9014 * Submission

---
author: 
- Sylvain Schmitt,
- on the behalf of the authors
opening: Dear Editor-in-chief,
closing: Sincerely,
address:
- "__Object__: Submission of a manuscript to Journal of Ecology"
return-address:
- Sylvain Schmitt
- Campus agronomique
- BP 316
- 97379 Kourou, French Guiana
output: linl::linl
---

>>>>

---
author: 
- Sylvain Schmitt & Bruno Hérault,
- on the behalf of the authors
opening: Dear Editor-in-chief,
closing: Sincerely,
address:
- "__Object__: Submission of a manuscript to Journal of Ecology"
return-address:
- Sylvain Schmitt & Bruno Hérault
- Campus agronomique
- BP 316
- 97379 Kourou, French Guiana
output: linl::linl
---
